The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-12-10 Paper.qmd
preparing to use public data; tweaks to pca plots

@@

# To use public data, comment out dataprep.R
# and uncomment load statement
source("dataprep.R")
# load("data/utilasignalingPublicData.rda")

source("analysis.R")
# source("analysis2.R") # Generates many plots. Slow!
```

>>>>

library(dplyr)
library(purrr)
library(stringr)
library(labelled)

load("data/m3_1e6_cost_freq.rda")

@@

# To use public data, comment out this line
source("dataprep.R")

# And uncomment this line
# load("data/utilasignalingPublicData.rda")

source("analysis.R")
source("analysis2.R") # Generates many plots. Slow!
```
